Predicting of the pulmunary TB cases using clinical

### 2024-05-05 code/eda-code/eda.qmd
part62

# Create a summary table with specified variable types
characteristics <- madaproject %>%
  select(all_of(variables), tb) %>%
  tbl_summary(
    by = tb,
    type = everything() ~ "categorical"
  )
characteristics <- data.frame(characteristics)
# Print the summary table
characteristics

>>>>

# Create a summary table with specified variable types
characteristics <- madaproject %>%
  select(all_of(variables), tb) %>%
  tbl_summary(
    by = tb,
    type = everything() ~ "categorical"
  )

# Convert tbl_summary object to data frame and assign column names
characteristics <- as.data.frame(characteristics)
column_names <- c("Characteristic", "No TB", "With TB")
names(characteristics) <- column_names

# Print the summary table
print(characteristics)
